MATD02 - Exploration of Finite Geometry

### 2024-11-18 paper/main.tex
Add marp presentation, fix small typo in bijection phi

        \underline{Case 2}: $L_1$ does not intersect $L_2$.
        Let $x \in L_1, y \in L_2$, then the line $L_3 \coloneqq xy$ intersects with both $L_1$ and $L_2$, so from case 1 we have bijections
        $\phi_1: L_1 \rightarrow L_3$ and $\phi_2: L_3 \rightarrow L_2$, and thus a bijection $\phi_1 \circ \phi_2: L_1 \rightarrow L_3$.
    \end{proof}

>>>>

        \underline{Case 2}: $L_1$ does not intersect $L_2$.
        Let $x \in L_1, y \in L_2$, then the line $L_3 \coloneqq xy$ intersects with both $L_1$ and $L_2$, so from case 1 we have bijections
        $\phi_1: L_1 \rightarrow L_3$ and $\phi_2: L_3 \rightarrow L_2$, and thus a bijection $\phi_1 \circ \phi_2: L_1 \rightarrow L_2$.
    \end{proof}
